Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
I got confused about opaque expression initially, because I read 'the continuation' as a general referece to any conditinuation used in the transformed code. I replaced it by 'continuation parameter' so as to emphasise that we mean a particular continuation argument, not any continuation.

Opaque, or value, expressions, have a different shape in the
original and the CPS form. However, their CPS form follows the
pattern \texttt{(continuation transformed-expression)}, and thus
the transformation does not depend on the continuation, and
can be accomplished without passing the continuation as a
transformation argument. Primitive (non-CPS) procedures used in
Anglican code, \texttt{(fn ...)} forms, and \text{(mem ...)}
forms are opaque and transformed by
\texttt{primitive-}\linebreak[0]\texttt{procedure-}\linebreak[0]\texttt{cps},
\texttt{fn-cps}, and \texttt{mem-cps}, correspondingly: a
slightly simplified CPS form of expression
\begin{lstlisting}[style=default]
(fn [x y]
  (+ x y))
\end{lstlisting}
would be
\begin{lstlisting}[style=default]
(fn [cont $state x y]
  (cont (+ x y) $state))
\end{lstlisting}
In the actual code an automatically generated fresh symbol is
used instead of \texttt{cont}.

@@

The most general form of CPS transformation receives an
expression and a continuation, and returns the expression
in CPS form with the continuation potentially called in multiple
tail positions. General expressions can be somewhat voluntarily
divided into several groups:
\begin{itemize}
    \item binding forms --- \texttt{let} and
        \texttt{loop/recur};
    \item flow control --- \texttt{if}, \texttt{when},
        \texttt{cond}, \texttt{case}, \texttt{and}, \texttt{or} and \texttt{do};
    \item function applications and \texttt{apply};
    \item probabilistic forms --- \texttt{observe},
        \texttt{sample}, \texttt{store}, and \texttt{retrieve}.
\end{itemize}
Functions that transform general expressions accept the
expression and the continuation as parameters, and are
consistently named \texttt{cps-of-}\textit{form}, for example,
\texttt{cps-of-do}, \texttt{cps-of-store}.

>>>>

Opaque, or value, expressions, have a different shape in the
original and the CPS form. However, their CPS form follows the
pattern \texttt{(continuation transformed-expression \$state)}, and thus
the transformation does not depend on the continuation parameter, and
can be accomplished without passing the parameter as a
transformation argument. Primitive (non-CPS) procedures used in
Anglican code, \texttt{(fn ...)} forms, and \text{(mem ...)}
forms are opaque and transformed by
\texttt{primitive-}\linebreak[0]\texttt{procedure-}\linebreak[0]\texttt{cps},
\texttt{fn-cps}, and \texttt{mem-cps}, correspondingly: a
slightly simplified CPS form of expression
\begin{lstlisting}[style=default]
(fn [x y]
  (+ x y))
\end{lstlisting}
would be
\begin{lstlisting}[style=default]
(fn [cont $state x y]
  (cont (+ x y) $state))
\end{lstlisting}
In the actual code an automatically generated fresh symbol is
used instead of \texttt{cont}.

@@

The most general form of CPS transformation receives an
expression and a continuation as parameters, and returns the expression
in CPS form with the continuation parameter potentially called in multiple
tail positions. General expressions can be somewhat voluntarily
divided into several groups:
\begin{itemize}
    \item binding forms --- \texttt{let} and
        \texttt{loop/recur};
    \item flow control --- \texttt{if}, \texttt{when},
        \texttt{cond}, \texttt{case}, \texttt{and}, \texttt{or} and \texttt{do};
    \item function applications and \texttt{apply};
    \item probabilistic forms --- \texttt{observe},
        \texttt{sample}, \texttt{store}, and \texttt{retrieve}.
\end{itemize}
Functions that transform general expressions accept the
expression and the continuation as parameters, and are
consistently named \texttt{cps-of-}\textit{form}, for example,
\texttt{cps-of-do}, \texttt{cps-of-store}.
